\documentclass[10pt,letterpaper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[compact]{titlesec}
\usepackage{enumitem}

\pagestyle{empty}

\titleformat{\section}{\filcenter\normalfont\Large\bfseries}{\thesection}{1em}{}%[]
\titleformat{\subsection}{\normalfont\large\bfseries}{\thesubsection}{1em}{\titlerule\vspace{.5ex}}%[]
\titleformat{\subsubsection}{\normalfont\normalsize\bfseries}{\thesubsubsection}{1em}{}%[]

\newlist{rlist}{description}{2}
\setlist[rlist,1]{font=\normalfont\itshape\space, noitemsep}
\setlist[rlist,2]{font=\normalfont\itshape\textendash\space, noitemsep}



\begin{document}

\section*{Shaked Elisha}
\begin{center}
	%{\Large \textbf{Shaked Elisha}}\\
	{\emph{School Address:} \ XXX xxxxxx Ave.\ \textbar\ Apt. XXX\ \textbar\ Pittsburgh, PA 15213}\\
	{\emph{Permanent Address:} \ XXXX xxxx xxxxxxx\ \textbar\ Yorba Linda, CA 92886}\\
	{\emph{Phone Number:} (949)xxx-xxxx\ \ \textbar\ \ \emph{Email:} email@gmail.com}
\end{center}

\subsection*{Education}
\begin{rlist}
	\item \textbf{University of Pittsburgh \hfill Pittsburgh, PA}
	\item \textit{Dietrich School of Arts and Sciences, Expected M.A. in Statistics \hfill 2018 - 2019}
	\item \textit{Dietrich School of Arts and Sciences, B.S. in Statistics \hfill 2014 - 2018}
	\begin{rlist}
		\item Minors: Economics, French
		\item Major GPA: %3.368 %\ \ \ Cumulative GPA: 3.151
		\item University Honors College, Emerging Leaders - Leadership Training, Completed Outside the Classroom Curriculum, Model UN, SEMF, Chabad
	\end{rlist}
\end{rlist}
\subsubsection*{Relevant Coursework}
\begin{rlist}
	\item Course 1
\end{rlist}

\subsection*{Experience}
\begin{rlist}
	\item \textbf{Johnson \& Johnson - Biosense Webster \hfill Irwindale, CA}
	\item \textit{Quality Process and Engineering Intern {\scriptsize(through Kelly Services)} \hfill June 2017 - August 2017}
	\begin{rlist}
		\item Led a project of finding discrepancies in logs of incoming equipment from an acquired company.
		\item Created a spreadsheet categorizing and accounting for all incoming equipment.
		\item Logged incoming equipment into calibration record.
	\end{rlist}
	\item \textbf{Johnson \& Johnson - Biosense Webster \hfill Irwindale, CA}
	\item \textit{RF Generator Product R\&D Intern {\scriptsize(through Kelly Services)} \normalsize\hfill June 2016 - May 2017}
	\begin{rlist}
		\item Defined Electro-Cardiology Therapeutic Ablation product requirements.
		\item Collected all requirements from different R\&D groups and aligned them in one delivery method.
		\item Worked with teams in the US and Israel to integrate IBM Rational DOORs.
		\item Reviewed,optimized, and performed quality analysis of R programs for code quality and performance.
		\item Worked remotely from September 2016 - May 2017 
	\end{rlist}
	\item \footnotesize\textbf{YLS Bakery Café \hfill Yorba Linda, CA}
	\item \footnotesize\textit{Barista \hfill June 216 - August 2016}
	\item \footnotesize\textbf{Build a Bear Workshop (Downtown Disney Branch) \hfill Anaheim, CA}
	\item \footnotesize\textit{Sales Associate \hfill May 2015 - August 2015}
	\item \footnotesize\textbf{H. Salt Fish and Chips \hfill Orange, CA}
	\item \footnotesize\textit{Waitress / Hostess \hfill June 2014 - September 2014}
\end{rlist}

\subsection*{Computer Skills}
\begin{rlist}
	\item[Languages] R, \LaTeX
	\item[Software] Minitab, SAS, IBM Rational DOORs, Microsoft Office Products (i.e. Excel, Word, PowerPoint), and Adobe Photoshop
\end{rlist}

\subsection*{Language Skills}
\begin{rlist}
	\item[English] Fluent (speaking, reading, writing)
	\item[Hebrew] Fluent (speaking, reading, writing)
	\item[French] Fluent (speaking, reading, writing)
	\item U.S. Citizen as of 2015 - U.S. Resident as of 2009
\end{rlist}

\subsection*{Volunteering}
\begin{rlist}
	\item Challah for Hunger – food prep for donation
	\item Assistant teacher to children’s self-defense classes
	\item Beach cleanups in Corona del Mar, Newport Beach
\end{rlist}


\end{document}
